---
title: "Report_Final_Assessment_Adrian_Minnig"
author: "Adrian Minnig"
date: "13.06.2023"
format: html
    fig-width: 8
    fig-height: 4
editor: source
---

## Introduction (Dataset-Info)

The dataset "ToothGrowth" already built into R was used for this assessment.

> The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery methods, orange juice or ascorbic acid (a form of vitamin C and coded as VC). [C. I. Bliss (1952). The Statistics of Bioassay](https://doi.org/10.1016/C2013-0-12584-6)

## Materials and Methods (Requirements in R(Studio)

Information on used versions of R(Studio) and packages installed to reproduce the data\
are summarized in the "sessionInfo" at the end of this report.

## Descriptive Statistics

The dataset "ToothGrowth" was first examined using the functions "view" and "str"

```{r}
view(ToothGrowth)
```

## Analysis

Do Normality Tests --\> if normal then do t-Test

if not normal --\> Wilcox Rangsum

Shapiro TEst is for small samples

Kolgomorov test is for samples larger than 50

## Discussion

## Running Code

sessioninfo()

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
